A Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}

### 2019-05-15 main.tex
Add references.

\begin{document}
%
\title{Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Akira Kawata\inst{1} \and
Atsushi Igarashi\inst{2}\orcidID{0000-0002-5143-9764}}
%
\authorrunning{A. Kawata, A. Igarashi}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Graduate School of Informatics, Kyoto University, Kyoto, Japan\\
\email{akira@fos.kuis.kyoto-u.ac.jp} \and
\email{igarashi@kuis.kyoto-u.ac.jp}
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}

@@

\begin{itemize}
   \item On Cross-Stage Persistence in Multi-Stage\cite{Hanada2014}
   \item Eliminating Array Bound Checking Through Dependent Types\cite{Xi98}
   \item MetaML and Multi-stage Programming with Explicit Annotations\cite{MetaML}
   \item Idris, a general-purpose dependently typed programming language: Design and implementation\cite{brady2013idris}
   \item A Logical Foundation for Environment Classifiers\cite{Tsukada}
   \item Environment classifiers\cite{taha2003environment}
   \item A framework for defining logics\cite{harper1993framework}
   \item The Design and Implementation of {BER} MetaOCaml - System Description\cite{oleg2014}
   \item Refined Environment Classifiers\cite{kiselyov2016refined}
   \item Staging with control: type-safe multi-stage programming with control operators\cite{oishi2017staging}
\end{itemize}

>>>>

\begin{document}
%
\title{A Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Akira Kawata\inst{1} \and
Atsushi Igarashi\inst{2}\orcidID{0000-0002-5143-9764}}
%
\authorrunning{A. Kawata, A. Igarashi}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Graduate School of Informatics, Kyoto University, Kyoto, Japan\\
\email{akira@fos.kuis.kyoto-u.ac.jp} \and
\email{igarashi@kuis.kyoto-u.ac.jp}
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}

@@

\begin{itemize}
   \item On Cross-Stage Persistence in Multi-Stage\cite{Hanada2014}
   \item Eliminating Array Bound Checking Through Dependent Types\cite{Xi98}
   \item MetaML and Multi-stage Programming with Explicit Annotations\cite{MetaML}
   \item Idris, a general-purpose dependently typed programming language: Design and implementation\cite{brady2013idris}
   \item A Logical Foundation for Environment Classifiers\cite{Tsukada}
   \item Environment classifiers\cite{taha2003environment}
   \item A framework for defining logics\cite{harper1993framework}
   \item The Design and Implementation of {BER} MetaOCaml - System Description\cite{oleg2014}
   \item Refined Environment Classifiers\cite{kiselyov2016refined}
   \item Staging with control: type-safe multi-stage programming with control operators\cite{oishi2017staging}
   \item \red{Partial evaluation and automatic program generation}\cite{jones1993partial}
   \item \red{Efficient multi-level generating extensions for program specialization}\cite{gluck1995efficient}
   \item \red{Dependent types in practical programming}\cite{xi1999dependent}

        Section of Application
   \item \red{A dependently typed assembly language}\cite{xi2001dependently}
   \item \red{Run-time code generation and Modal-ML}\cite{wickline1998run}
   \item \red{C and tcc: a language and compiler for dynamic code generation}\cite{poletto1999c}
   \item \red{Run-time bytecode specialization}\cite{masuhara2001run}
   \item \red{A tour of Tempo: A program specializer for the C language}\cite{consel2004tour}
   \item \red{Optimizing ML with run-time code generation}\cite{lee1996optimizing}
   \item \red{Efficient incremental run-time specialization for free}\cite{marlet1999efficient}

\end{itemize}
